---
title: "p8105_hw5_yy3296"
author: "Yuze Yuan"
date: "`r Sys.Date()`"
output: github_document
---

```{r}
library(tidyverse)
library(readr)
```

## Problem 1

The code chunk below imports the data in individual spreadsheets
contained in `./data/zip_data/`. To do this, I create a dataframe that
includes the list of all files in that directory and the complete path
to each file. As a next step, I `map` over paths and import data using
the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("./data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn’t tidy – data are wide rather
than long, and some important variables are included as parts of others.
The code chunk below tides the data using string manipulations on the
file, converting from wide to long, and selecting relevant variables.

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```


Finally, the code chunk below creates a plot showing individual data,
faceted by group.

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

## Problem 2

I import the data

```{r}
homecide_raw = read_csv("./data/homicide-data.csv")
```

* Description
  * There are `r nrow(homecide_raw)` observations in the raw data.
  * There are `r ncol(homecide_raw)` variables in the raw data, which are `r colnames(homecide_raw)`.

I Create a city_state variable and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r}
summarize_homecide = 
  homecide_raw %>%
  janitor::clean_names() %>%
  mutate(city_state = str_c(city, ",", state)) %>%
  group_by(city_state) %>% 
  summarize(number_homecide = n(),
            unsolve_homecide = sum(disposition == "Closed without arrest" | disposition == "Open/No arrest"))
```

I use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object. And make some descriptions about the estimated proportion and confidence intervals from the resulting tidy dataframe. 

```{r}
Baltimore = 
  summarize_homecide %>%
  filter(city_state == "Baltimore,MD")
prop_Baltimore = prop.test(Baltimore$unsolve_homecide, Baltimore$number_homecide) %>%
  broom::tidy()
```
* For the city of Baltimore, MD, the estimated proportion of homicides that are unsolved is `r prop_Baltimore[['estimate']]`.
* The confidence interval is (`r prop_Baltimore[['conf.low']]`, `r prop_Baltimore[['conf.high']]`)

I run prop.test for each of the cities in the dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. I Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest to create a tidy dataframe with estimated proportions and CIs for each city.

```{r}
prop_allcities = 
  summarize_homecide %>% 
  mutate(
    prop_eachcity = map2(.x = unsolve_homecide, .y = number_homecide, ~prop.test(x = .x, n = .y)),
    tidy_prop_eachcity = map(.x = prop_eachcity, ~broom::tidy(.x))
    ) %>%
  unnest(tidy_prop_eachcity) %>% 
  select(city_state, estimate, conf.low, conf.high)
```
